\section{Introduction}
\label{introduction}

Articular cartilage is flexible connective tissue that permits
stability and movement of the skeleton.  This connective tissue
consists of an extracellular matrix (composed primarily of collagen,
elastin and proteoglycans) and one type of cell---the {\em
chondrocyte}---which is responsible for synthesis and homeostasis of
the matrix.  Under abnormal conditions, chondrocyte damage may occur
and the balance between matrix synthesis and degradation is lost,
causing inflammation of the tissue and/or osteoarthritis: a wearing
out of the cartilage layer which causes painful, bone-against-bone
friction.

It is generally known that the progression of osteoarthritis (Rush and
Hall, 2003) and limited recovery of chondrocytes (Jones et al, 1999)
is linked to poorly-regulated volume changes \citep{Lewisetal2011} and
physical damage to cartilage is easier in the context of reduced
osmolarity (Bushet et al, 2005).  In turn, there is indication that
these volume changes are linked to abnormal maintenance of resting
membrane potential in these cells \citep{Lewisetal2011}.  In unhealthy
cells, the response to challenging external stimuli may change
(e.g. much larger changes in resting membrane potential) (Lewis et al,
2011; WIlson, et al 2004; Tsuga 2002; Tirabashi 2010a).  It has been
suggested that these changes in the regulation of the resting membrane
potential are due to altered ion channel function (Lewis et al, 2011;
WIlson, et al 2004; Tsuga 2002; Tirabashi 2010a).  Direct experimental
investigation of the link between chondrocyte electrophysiology and
chondrotoxicity is complicated, however, by chondrocytes' small cell
size and the associated limitations of in vitro electrophysiological
studies (cite?).  We have thus developed and present here a detailed,
biophysically-based model of chondrocyte electrophysiology.  The first
of its kind, the model will facilitate investigation of questions
related to chondrocyte electrophysiology and signaling, and provides a
profound basis for subsequent models of chondrocyte and articular
pathophysiology.

Osteoarthritic changes may develop in even young patients following
orthopedic surgery (cite) via chondrolysis, a condition in which
accelerated loss of articular cartilage occurs over a short time
period (Webb editorial, 2009).  Several clinical studies have
suggested that this significant chondrotoxicity can occur as a result
of postoperative administration of bupivacaine, a local anesthetic
(Busfield and Romero, 2009; Bailie and Ellenbecker, 2009; Rapley et
al, 2009; Wiater, et al, 2011).  Experimental work has confirmed that
bupivacaine reveals profound chondrotoxic effects in both cell
\citep{Chuetal2006} and animal studies (Gomoll et al, 2006; Chu et al,
2010).  The exact mechanisms leading to chondrotoxicity in this
context remain unclear.  However, it appears that the mechanism of
toxicity is unrelated to the primary mechanism of action of
bupivacaine, the blockade of voltage-gated sodium channels (cite), and
instead may be related to potassium channel blockade (Grishko, et al,
2010).  Additionally, it is known that the family of two-pore K+
channels, recently identified in human articular chondrocytes (Clark,
et al, manuscript) is likely affected by bupivacaine administration
(Clark et al, manuscript; Punke et al 2003).  We therefore hypothesize
that the blockade of the two-pore K+ channel in human articular
chondrocytes by the local anesthetic bupivacaine leads to abnormal
regulation of the resting membrane potential in these cells, which may
concomitantly lead to abnormal volume regulation, altered signaling,
and cell death.  The aims of this paper are: (1) to present a novel
model of chondrocyte electrophysiology in detail and, (2) to use this
model to investigate the role of bupivacaine in the homeostasis of the
chondrocyte resting membrane potential.

\todo{Merge the following notes further motivating the model with the
  preceding introductory text}

Chondrocytes are the metabolically-active cells found in mature
articular cartilage \citep{BarrettJolleyetal2010}. Articular cartilage
is aneural, avascular, alymphatic connective tissue that covers the
articulating ends of diarthroidal joints \citep{Poole1997,
Mankin1982}. Articular cartilage is thus regularly exposed to
mechanical stresses, and this exposure is essential for the health of
the tissue \citep{Stockwell1991}. Chondrocytes occupy only 1--10\% of
the total volume of articular cartilage in mammals
\citep{CarneyMuir1988, Halletal1996} and play no direct mechanical
role. Mechanical response is provided by the extra-cellular matrix
(ECM) of articular cartilage. The ECM is composed of (a) collagen
fibers, which gives the tissue the ability to resist tension (b)
negatively-charged gel-like proteoglycans (PGs) trapped within the
collagen mesh, allowing the tissue to bear compression
\citep{Poole1997, BuckwalterMankin1998} and (c) synovial fluid within
the articular capsule which acts as a lubricant, allowing for free
movement of the bones \citep{Edwardsetal1994}. The chondrocyte thus
resides in an atypical and dynamic environment and its primary role is
to maintain of viable cartilage tissue by balancing macromolecular
synthesis and breakdown (see e.g. \citet{Wilkinsetal2000,
Stockwell1991, Fassbender1987}). Chondrocytes, like all other cells,
must possess effective membrane transport systems to minimise changes
of cellular composition (in particular, cell volume, pH and ionic
content) in the face of fluctuating surroundings \citep{Halletal1996,
  Mobasherietal1998, Stein1990}. The broad goal of our model is to
explore some of these channels.

% Local Variables:
% TeX-master: "chondrocyte-model"
% mode: latex
% mode: flyspell
% End:
